Data Visualization

### 2018-05-31 scripts/5_data_viz.Rmd
Title Change and Final updates for anonymous submission

---
title: "5_data_viz"
author: "Andy Krause"
date: "May 10, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

   ggplot(rev_df,
          aes(x=revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=dens_cols) +
    scale_color_manual(values=dens_cols) +
    ggtitle('Short Term Revenue vs Long Term Revenue') +
    xlab('Annual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000))

>>>>

---
title: "Data Visualization"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

   ggplot(rev_df,
          aes(x=revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=dens_cols) +
    scale_color_manual(values=dens_cols) +
    ggtitle('Revenue Comparison: Short Term vs Long Term Properties') +
    xlab('Annual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000))
